### 2019-02-12 sections/relatedwork.tex
Updated related work section with subsections

@@

Much research has been done into workflow patterns. They are regarded as special
kind of the design patterns in software engineering. They identify recurring patterns
in workflow systems, much like the combinators defined by \TOPHAT. Work by
Van der Aalst~\cite{journals/dpd/AalstHKB03} defines a comprehensive list of
these pattens, and examines their availability in industry workflow software.
Workflow patterns are usually described in terms of control flow graphs, and no
formal specification is given, which makes comparison and formal reasoning more
difficult.

\paragraph{Petri net}

Petri nets, and more specifically Workflow nets, have also been used to describe
workflows~\cite{journals/jcsc/Aalst98}. They allow for the modelling and
analysis of business processes. A downside of using workflow nets is that the
model is not directly implementable, which is possible with the \TOPHAT calculus.

% NEW RELATED WORK sections

\paragraph{Business process modeling}

A plethora of languages exists to describe, model, display and execute these
processes. YAWL by van der Aalst~\cite{DBLP:journals/is/AalstH05} is one of
these languages. It facilitates modeling and execution of dynamic workflows,
with support for AND, OR and XOR workflow patterns. YAWL programs consist of
Nets, and are therefore programmed visually. BPEL\todo{cite} is another popular business process language.
The standardized language allows for the specification of actions within
business processes, using an XML format. Processes specified in BEPL are
executable, just like YAWL.

>>>>

\subsection{Worfklow modeling}

Much research has been done into workflow modeling. These works focus on
describing the collaboration between subsystems, rather than the communication
between them.

@@

Workflow patterns are regarded as special kind of the design patterns in
software engineering. They identify recurring patterns in workflow systems, much
like the combinators defined by \TOPHAT. Work by Van der
Aalst~\cite{journals/dpd/AalstHKB03} defines a comprehensive list of these
pattens, and examines their availability in industry workflow software.
Workflow patterns are usually described in terms of control flow graphs, and no
formal specification is given, which makes comparison and formal reasoning more
difficult.

\paragraph{Workflow nets}

Workflow nets~\cite{journals/jcsc/Aalst98} allow for the modeling and analysis
of business processes. They are graphical in nature, and clearly display how
every component is related to each other. A downside of Workflow nets is that
they do not facilitate higher order constructs and that they are often not
directly executable.

\paragraph{YAWL}

This is not always the case however. A language based on workflow nets that is
actually directly executable is YAWL by van der
Aalst~\cite{DBLP:journals/is/AalstH05}. It facilitates modeling and execution of
dynamic workflows, with support for AND, OR and XOR workflow patterns. As
mentioned, YAWL programs consist of Workflow Nets, and are therefore programmed
visually.

\paragraph{BPEL}

BPEL\todo{cite} is another popular business process language. The standardized
language allows for the specification of actions within business processes,
using an XML format. Processes specified in BEPL are executable, just like YAWL.

\subsection{Related web services}
